Automating Verification of MPC Security

### 2023-06-09 popl24/pmf.tex
checkpoint

\paragraph{Example \ref{example-he} revisited} This standard example
of an MPC secure protocol illustrates how a functionality- in this
case addition (in the binary field)- can be implemented securely. As
mentioned previously, it is \emph{not} the case that \emph{no}
information about input secrets can be revealed to the adversary in
the MPC threat model, since the result of the functionality can itself
reveal information. For example, if the result of addition is $0$,
the adversary knows that all clients must have the same value.
More precisely:
\begin{mathpar}
  (\sum_{\beta}(\progd(\prog_{\ref{example-he}}))(\{\sx{1}{1} \mapsto \beta, \sx{2}{1} \mapsto \beta, \sx{3}{1} \mapsto \beta \}|\{ \vx{0}{output} \mapsto 0 \})) = 1
\end{mathpar}

>>>>

\paragraph{Example \ref{example-he} revisited} This standard example
of an MPC secure protocol illustrates how a functionality- in this
case addition (in the binary field)- can be implemented securely. As
mentioned previously, it is \emph{not} the case that \emph{no}
information about input secrets can be revealed to the adversary in
the MPC threat model, since the result of the functionality can itself
reveal information. For example, if the result of addition is $0$,
the adversary knows that two of the clients' secrets must be 0
and the third's must be 1, though not whose is whose- so we can
observe:
\begin{mathpar}
  (\progd(\prog_{\ref{example-he}}))(\{\sx{1}{1} \mapsto 0, \sx{2}{1} \mapsto 1, \sx{3}{1} \mapsto 0 \}|\{ \vx{0}{output} \mapsto 0 \}) = .33
\end{mathpar}
Further, since the standard MPC threat model allows partipating
clients to be corrupted we can formally consider the impacts on
information released to the adversary by conditioning the program
distribution on corrupt secrets.  So if we assume client 2
with input secret 1 is corrupted, and we assume the output is 0, then
adversary knows with certainty that clients 1 and 3 both have input
secrets 0. We can express this as:
$$
\progd(\prog_{\ref{example-he}}))(\{\sx{1}{1} \mapsto 0, \sx{3}{1} \mapsto 0 \}|\{ \sx{2}{1} \mapsto 1, \vx{0}{output} \mapsto 0 \})
= 1
$$ A critical point to note is that this information revealed to the
adversary does not violate MPC security- under the assumption of
public release of the functionality result, and under the assumption
of the possible corruption of clients, this is the cost of doing
business. Rather, the concern is that the protocol does not release
any additional information through information communicated to views
of corrupted parties. Additive secret sharing as realized in
$\prog_{\ref{example-he}}$ is MPC secure in this sense- so for
example, for any $\beta_1$ and $\beta_2$ we have:
$$
\begin{array}{c}
\progd(\prog_{\ref{example-he}}))(\{\sx{1}{1} \mapsto 0 \}|\{ \sx{2}{1} \mapsto 0, \vx{0}{output} \mapsto 0 \})
= \\
\progd(\prog_{\ref{example-he}}))(\{\sx{1}{1} \mapsto 0 \}|\{ \vx{2}{s1} \mapsto \beta_1, \vx{2}{s3} \mapsto \beta_2, \sx{2}{1} \mapsto 0, \vx{0}{output} \mapsto 0 \})
= \\
.5
\end{array}
$$
